### 2016-02-17 README.Rmd
pass check
fix warnings, update readme

## eml2

>>>>

[![Travis-CI Build Status](https://travis-ci.org/cboettig/eml2.svg?branch=master)](https://travis-ci.org/cboettig/eml2)

# eml2

*Note*: `eml2` is work in progress. Please see the Issues tracker in this repository for details about current issues and development milestonds.

## Installation

`eml2` has not yet been released.  Please install from GitHub after installing the `devtools` package (from CRAN):

```{r eval=FALSE}
devtools::install_github("cboettig/eml2")
```

## Quickstart

Load the package and read in an EML file:

```{r}
library("eml2")
f <- system.file("xsd/test/eml.xml", package = "eml2")
eml <- read_eml(f)
```

This creates a native R object called `eml`.  Although this is an "S4 object" type, it uses a "show"
method which displays in an XML-like layout for convenience:

```{r}
eml
```

Validate EML against the official schema

```{r}
eml_validate(eml)
```

Write out as EML:

```{r}
write_eml(eml, "example.xml")
```

```{r include=FALSE, echo=FALSE}
unlink("example.xml")
```

## Manipulating EML objects

Eventually `eml2` will provide constructor and extract methods to create and extract common metadata sections from convenient R stuctures (e.g. `data.frames` with unit metadata, common R classes like `Person`, `bibtype`).  For now, the only method to access and modify EML is to use the standard S4 subsetting and constructor methods.

Our current example does not have a publication date.  Let's add one:

```{r}
eml@dataset@ResourceGroup@pubDate <- new("pubDate", "2016")
```

Note that we use the constructor method `new()` to create an object.

### Working with repeating elements
